%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Yue}
\familyname{Tian (Alex)}
\mobile{(585)354-1956}                    % optional, remove the line if not wanted
\email{alexyuetian@gmail.com}                      % optional, remove the line if not wanted
\homepage{softdrunk.me}                % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Skills}
\cvline{Languages}{Python = C > Java > Ruby > C++}
\cvline{Technologies}{ETW, Rails, MySQL, Redis, AWS, \LaTeX{}, Git, Vim, Mac OSX, Ubuntu, Windows}
\section{Education}
\cventry{2013-Present}{BA, Computer Science}{University of California,
Berkeley}{}{}{}
\cvline{GPA:}{\small 3.77/4.0}

\section{Experience}

\cventry{2015}{Software Developer Intern}{Google}{Montreal, Canada}{}{
  \begin{itemize}
    \item Project: Chrome startup I/O investigation and experimentation
    \item Implemented a tool that automates the profiling of Chrome's cold
      startup (resources not in memory) through emptying the standby list on
      Windows programmatically.
    \item Hunted down two major I/O culprits to user profiles that slow Chrome
      down on startup.
    \item Achieved roughly 40\% speedup on startups with cold profiles by
      modifying the browser code locally.
  \end{itemize}
}

\cventry{2014}{Software Development Engineer}{Sobrr}{San Francisco, CA}{}{
  \begin{itemize}
    \item Full stack developer at Sobrr, a tech startup that has reached over
      300k activated users globally.
    \item Built and optimized the backend for several major features including
      group chat, hashtags, member taggings, etc, using Ruby on Rails and Redis
      cache.
    \item Built an analysis tool in python to reverse geocode and
      aggregate member location data.
  \end{itemize}
}

\cventry{2013}{Research Intern}{Visual Computing Group, Harvard
University}{Cambridge, MA}{}{
  \begin{itemize}
    \item Built a graphical interface with C++ and OpenCV to feed data of
      hand-anatated cell membranes to gentle boosting algorithms that trains
      the machines for automated annotation.
  \end{itemize}
}

\section{Personal Projects}

\cventry{Grue}{Event-planning app that connects university organizations with
potential members}{}{}{}{
  \begin{itemize}
    \item Built the marketing website with Jquery, CSS, and HTML.
    \item Deployed cloud code on Parse to allow email sign-ups and maintenance
      tasks.
  \end{itemize}
}

\section{Relevant Coursework}
\cvline{Computer Science}{Security (taking), Database Systems (taking), Machine
Learning, Operating Systems, Internet Architecture and Protocols, Efficient
Algorithms and Intractable Problems, Artificial Intelligence, Structure and
Interpretation of Computer Programs, Data Structures, Computer Architecture}
\cvline{Math}{Linear Algebra and Differential Equations, Discrete Mathematics
and Probability Theory}

\section{Honors}
\cventry{2013}{Dean's Honor}{}{}{}{Acknowledges the academic achievement of the
top 4 percent of Letters and Science students}
\cventry{2012}{New York State Math Competition High Scorer}{}{}{}{Top 200 scorers in the state math meet}
\cventry{2012}{American Invitational Mathematics Examination
Qualifier}{}{}{}{Ranked top 5 percent on the AMC12 high school mathematical
contest, qualified for AIME}


\end{document}
